Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-05-04 paper.tex
Add references

(TODO: where to put this paragraph?)
A study of recent changes to memory management in Linux has found that there has
been a lot of focus on improving the scalability of data structures used in the
Linux memory manager (TODO cite: Huang et. al. ATC'16). Since systems with
persistent memory are expected to have large amounts of memory, there have been
efforts to reduce the overheads of struct page. This is because these structures
can consume several gigabytes of memory for systems with terabytes of persistent
memory (TODO cite: https://lwn.net/Articles/640113/). These structures need to
be stored in volatile memory not only because they need to be accessed quickly
for performance reasons, but also to avoid wearing out of persistent memory due
to frequent writes to this data structure. Patches proposed to the Linux kernel
have proposed getting rid of the struct page altogether, but the complexity
associated with such radical changes have hindered their acceptance by the
community. Other works such as RadixVM \cite{radixvm} have also approached
scalability with respect to the number of cores in the system.

>>>>

(TODO: where to put this paragraph?)
A study of recent changes to memory management in Linux has found that there
has been a lot of focus on improving the scalability of data structures used in
the Linux memory manager \cite{huang2016evolutionary}. Since systems with
persistent memory are expected to have large amounts of memory, there have been
efforts to reduce the overheads of struct page. This is because these
structures can consume several gigabytes of memory for systems with terabytes
of persistent memory \cite{corbet_persistent_progress}. These structures need
to be stored in volatile memory not only because they need to be accessed
quickly for performance reasons, but also to avoid wearing out of persistent
memory due to frequent writes to this data structure. Patches proposed to the
Linux kernel have proposed getting rid of the struct page altogether, but the
complexity associated with such radical changes have hindered their acceptance
by the community. Other works such as RadixVM \cite{radixvm} have also
approached scalability with respect to the number of cores in the system.
